Limited physiological plasticity and reduced relative variance in physiological rates of ectotherm populations under climate change

### 2024-07-09 ms.qmd
Fixed supp table lnVR which should now have mx temp and a slope random effect

####################################################
  # Model 4.3: Model environmental variability by acute/acclim
####################################################
rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.3          <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + type + type:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)

@@

 # Extract the fixed / population-level effect summaries of the posterior
    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
    rownames(fixed) <- NULL

 # Extract the random effect summaries of the posteriors (SDs)
    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
    rownames(random) <- NULL

@@

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```

>>>>

####################################################
  # Model 4.3: Model environmental variability by acute/acclim
####################################################
rerun = FALSE
if(rerun){
  # More realistic model with 
  model4.3          <- metafor::rma.mv(effect_size ~ max_temp_c + c_accl_time + cv_c + type + type:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_cvr), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data_wild)

   model4.3_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + cv_c + type + type:cv_c + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + c_accl_time + type + habitat + type:habitat + 
        (~1 | record_num) + 
        (1 | gr(species_full, cov = A_VR)) + 
        (1 + max_temp_c| spp) + 
        (1|trait), 
        data2 = list(A_VR=A_VR), family = gaussian(), 
        prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), 
        control = list(adapt_delta = 0.98, max_treedepth = 12), 
        chains = 4, thin = 5, iter = 8000, warmup = 1000, cores = 4, data = lnVRQ10_data)

@@

 # Extract the fixed / population-level effect summaries of the posterior
    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
    fixed <- cbind(Parameter = c("Intercept", "Mximum Temperature (centered)", "Acclimation Time (centered)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
    rownames(fixed) <- NULL

 # Extract the random effect summaries of the posteriors (SDs)
    random <- rbind(header = rep(0, 4), do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x))))
    random <- cbind(Parameter = c(" ", "Study", "Phylogeny", "Species (intercept)", "Species (slope max temp)", "Trait"), random)
    rownames(random) <- NULL

@@

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 10)
```
